An efficient feedback calibration algorithm for direct imaging radio telescopes

### 2016-03-07 cal_demo/ms.tex
Adding comments on other calibration regimes, adding hera memo 10 to bib

When using the single point source model, all calibration methods trend downward until they reach an error floor due to the confusion sources that were not modeled. The EPICal and visibility-based solutions reach a similar floor, but EPICal achieves a marginally lower level (on average 5\% lower). This can be attributed to the same reason EPICal underperformed with the full sky model: EPICal only used a single pixel in the sky to form its solutions. When using the full sky model, it was down weighting the information in the rest of the sky. But when the sky model only contains the bright point source, the single pixel used in EPICal is the location where this model is most accurate, effectively down weighting the pixels with incomplete sky model.

>>>>

The exact ratio of EPICal gain noise to visibility-based gain noise depends on the fraction of the total sky power contained in our calibrator source. In the example here, our calibrator accounted for 22\% of the total sky power. We repeated the experiment in the regime where the calibrator dominated the sky and found that the difference in EPICal and visibility-based error goes to zero, as expected. For a typical HERA observation, the sky temperature is expected to by about 180~K \citep{jac15}, and a bright calibrator source could be about 10\% of this power. In this regime we found that EPICal gain noise was about 60\% higher than visibility-based gain noise for the same effective integration time.

When using the single point source model, all calibration methods in figure~\ref{fig:errors} trend downward until they reach an error floor due to the confusion sources that were not modeled. The EPICal and visibility-based solutions reach a similar floor, but EPICal achieves a marginally lower level (on average 5\% lower). This can be attributed to the same reason EPICal underperformed with the full sky model: EPICal only used a single pixel in the sky to form its solutions. When using the full sky model, it was down weighting the information in the rest of the sky. But when the sky model only contains the bright point source, the single pixel used in EPICal is the location where this model is most accurate, effectively down weighting the pixels with incomplete sky model. In the regime typical of HERA discussed above, EPICal's error floor was 10\% lower than that of visibility-based solutions.
